---
title: "MA678_Udemy"
author: "Xiaojia Liu"
output: pdf_document
---

```{r setup, include=FALSE}
library(quantmod)
library(RcppBDT)
library(tidyverse)
library(caret)
library(timeDate)
library(lubridate)
library(PerformanceAnalytics)
library(rstanarm)
library(lme4)
```

### Load Data
```{r}
udemy_original <- read.csv("udemy_original.csv")
nrow(udemy_original)
head(udemy_original)
summary(udemy_original)

#Explore why there're 1403 NAs in discount_price__amount
#while no NA in discount_price__currency & discount_price__price_string
udemy_discountNA <- udemy_original[is.na(udemy_original$discount_price__amount),]
head(udemy_discountNA)
udemy_priceNA <- udemy_original[is.na(udemy_original$price_detail__amount),]
head(udemy_discountNA)
```

### EDA & Data Processing
1 - Assign NA to correspond empty value.
2 - Replace NA with 0 for numerical varibles.
```{r}
udemy_original$url <- NULL
n = nrow(udemy_original)
for(i in 1:n){
  if(is.na(udemy_original$discount_price__amount[i])){
    udemy_original$discount_price__amount[i] <- 0
    udemy_original$discount_price__currency[i] <- NA
    udemy_original$discount_price__price_string[i] <- NA
  }
}

for(i in 1:n){
  if(is.na(udemy_original$price_detail__amount[i])){
    udemy_original$price_detail__amount[i] <- 0
    udemy_original$discount_price__currency[i] <- NA
    udemy_original$price_detail__price_string[i] <- NA
  }
}
```

```{r}
summary(udemy_original)
rm(udemy_discountNA)
rm(udemy_priceNA)
# In the following session, use udemy only
udemy <- udemy_original
```



### More on EDA
## Look into the numeric values
```{r}
udemy_numerical <- subset(udemy, select = c(id, num_subscribers, avg_rating, avg_rating_recent, rating, num_reviews, num_published_lectures, num_published_practice_tests, price_detail__amount))
chart.Correlation(udemy_numerical, histogram = TRUE, pch = 19)

```
There might be some correlation between number of subscribers and number of reviews.  
The num_published_lectures (cor = 0.21) might be slight related.  

## M1 - subscribers vs reviews
```{r}
udemy_M1 <- as.data.frame(cbind(subscribers = udemy$num_subscribers, reviews = udemy$num_reviews))
head(udemy_M1)
#chart.Correlation(udemy_M1, histogram = TRUE, pch = 19)

ggplot(udemy_M1, aes(x=reviews, y=subscribers)) + geom_bar(stat="identity", fill="steelblue") + ggtitle("Barplot of subscribers vs reviews")
ggplot(udemy_M1, aes(x=reviews, y=subscribers)) + geom_point(size = 0.5, alpha = 0.2) + geom_smooth(method='lm') + ggtitle("Linear Regression of subscribers vs reviews")

#if look only at the reviews < 10000
udemy_M1.2 <- subset(udemy_M1, udemy_M1$reviews<10000)
ggplot(udemy_M1.2, aes(x=reviews, y=subscribers)) + geom_bar(stat="identity", fill="steelblue") +  ggtitle("Barplot of subscribers vs reviews [reviews < 10000]")
ggplot(udemy_M1.2, aes(x=reviews, y=subscribers)) + geom_point(size = 0.5, alpha = 0.2) + geom_smooth(method='lm') + ggtitle("Linear Regression of subscribers vs reviews [reviews < 10000]")
```

## M2 - subscribers vs published lectures
```{r}
udemy_M2 <- as.data.frame(cbind(subscribers = udemy$num_subscribers, publish = udemy$num_published_lectures))
ggplot(udemy_M2, aes(x=publish, y=subscribers)) + geom_bar(stat="identity", fill="steelblue") +  ggtitle("Barplot of subscribers vs published lectures")
ggplot(udemy_M2, aes(x=publish, y=subscribers)) + geom_point(size = 0.5, alpha = 0.2) + geom_smooth(method='lm') + ggtitle("Linear Regression of subscribers vs published lectures")
```

### M3 - Multi-Regression with subscribers vs num_reviews * num_published_lectures 
Observe that, there might be some correlation between num_reviews and num_published_lectures.   
Intuitively, the more published_lectures available, the more reviews users tend to leave.  
```{r}
udemy_M3 <- as.data.frame(cbind(subscribers = udemy$num_subscribers, reviews = udemy$num_reviews, publish = udemy$num_published_lectures))
y = udemy_M3$subscribers
x1 = udemy_M3$reviews
x2 = udemy_M3$publish

M3.1 <- glm(y ~ x1 * x2, data = udemy_M3)
summary(M3.1)
coefficients(M3.1)

udemy_M3.2 <- as.data.frame(cbind(subscribers = udemy_M1.2$num_subscribers, reviews = udemy_M1.2$num_reviews, publish = udemy_M1.2$num_published_lectures))
M3.2 <- glm(y ~ x1 * x2, data = udemy_M3.2)
summary(M3.2)
coefficients(M3.2)
```

### M4 - Multilevel linear models
```{r}
M4.1 <- lmer(y ~ x1 + (1 | x2), data=udemy_M3)
summary(M4.1)
M4.2 <- lmer(y ~ x1 + (1 | x2), data=udemy_M3.2)
summary(M4.2)
```



### Cross Validation
```{r}
set.seed(123)
training.samples <- udemy_M3$subscribers %>% createDataPartition(p = 0.8, list = FALSE)
train.data  <- udemy_M3[training.samples, ]
test.data <- udemy_M3[-training.samples, ]


#M3.1
predictions <- M3.1 %>% predict(test.data)
data.frame(RMSE = RMSE(predictions, test.data$subscribers), MAE = MAE(predictions, test.data$subscribers))
#M4.1
predictions <- M4.1 %>% predict(test.data)
data.frame(RMSE = RMSE(predictions, test.data$subscribers), MAE = MAE(predictions, test.data$subscribers))
```













